Neural Networks as Dual Gaussian Processes for Sequential Learning

### 2023-09-18 papers/iclr-2024/main.tex
added some citation stuff

\subsection{Related work}
\label{sec:related}
%
% General Bayesian deep learning
\textbf{Bayesian deep learning}
Probabilistic methods in deep learning~\citep{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each with its own set of strengths and weaknesses.

>>>>

\subsection{Related work}
\label{sec:related}
%
% General Bayesian deep learning
\textbf{Bayesian deep learning}
Probabilistic methods in deep learning~\citep{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \citep{kendall2017what,wilson2020bayes}) and model selection (\eg,~\citep{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \citep{blei2017variational}, deep ensembles \citep{lakshminarayanan2017simple}, MC dropout \citep{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each with its own set of strengths and weaknesses.
